Bias no more: A practical guide to latent group-mean centering in longitudinal and other hierarchical bayesian models

### 2022-12-07 ms.Rmd
Safer parallelization

# HMC and parallel computation options
MAX_CORES <- as.numeric(Sys.getenv("MAX_CORES"))
if (is.na(MAX_CORES)) MAX_CORES <- parallel::detectCores(logical = FALSE)
THREADS <- 1
CORES <- MAX_CORES
ITER <- 10000
if (require(cmdstanr)) {
  options(brms.backend = "cmdstanr")
  THREADS <- MAX_CORES %/% 4
}

>>>>

# HMC and parallel computation options
MAX_CORES <- as.numeric(Sys.getenv("MAX_CORES"))
if (is.na(MAX_CORES)) MAX_CORES <- parallelly::availableCores(logical = FALSE)
THREADS <- 1
ITER <- 10000
CHAINS <- 4
if (require(cmdstanr)) {
  options(brms.backend = "cmdstanr")
  THREADS <- MAX_CORES %/% CHAINS
}
